---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
install.packages(rtweet)
library(rtweet)
```

```{r}
codeclan_tweets <- read_csv("data/code_clan_info.csv")
codeclan_tweets
```
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.

Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

Find the mean number of characters that a CodeClan tweet contains.

The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.
```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```















