---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
install.packages(rtweet)
library(tidyr)
library(plyr)
```






Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

1. Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
codeclan_tweets <- read_csv("data/code_clan_tweets.csv")
codeclan_tweets

dim(codeclan_tweets)
names(codeclan_tweets)
head(codeclan_tweets)
```


2. First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.

```{r}
boxplot(codeclan_tweets$favorite_count)
```




3. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
count(codeclan_tweets$is_quote)
```

4. Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}

retweet_source <- codeclan_tweets %>% 
  select(retweet_count, source) %>% 
  mean(retweet_count) %>% 
  summarise(retweet_count = n()) %>% 
  arrange(desc(retweet_count))
  
retweet_source

```


5. Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
no_of_likes <- drop_na(favorite_count) %>% 
count(codeclan_tweets, vars = favorite_count, wt_var = media_type)

```


6. Find the mean number of characters that a CodeClan tweet contains.

```{r}
nchar("tweet")
```


7. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.


```{r}

read_csv("data/code_clan_info.csv") <- codeclan_info

left_join(codeclan_tweets, codeclan_info)
```


8. From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.
```{r}

pattern <- "#[a-z]*"

strings %>% 
  str_extract_all(codeclan_tweets)
  

```
Not
```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```















