---
title: "R Notebook"
output: html_notebook
---

2.Seed the wrestling database from the file wrestling.sql using the psql PostgreSQL command line interface.


```{r}
Sys.getenv("HOME")
```

```{r}

home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)
```

```{r}

library(RPostgreSQL)

```

3. Create a connection to the local wrestling database from R.
Pass the argument max.con = 2 to PostgreSQL() to make sure you don’t have too many simultaneous connections. We’ll be setting up a local connection and perhaps a remote connection, hence ‘2’.


```{r}
#my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), user = postgresql_username, password = postgresql_password, dbname = 'wrestling', host = 'localhost')
```

Remember to add a separate ‘disconnect’ block of code. We’ll write queries between the ‘connect’ and ‘disconnect’ block

```{r}
#dbDisconnect(conn = my_db_connection)
```



4. Using the R connection you just created, write and execute a SQL query to return all the wrestlers in the wrestlers table.

```{r}
View(wrestlers)
```

5. Explore the columns stored in the table. State which data type you think each column stores.
```{r}
Born - Character
Name - Character
Gender - Character (Logical)
Win Percent - Double
Total Matches - integer


```

```{r}
dbDisconnect(conn = my_db_connection)
```


1.2 Remote PostgreSQL Connections

Here are the details of the remote PostgreSQL database we wish to connect to:

Store the credentials above in appropriately named variables in your credentials.R file in your home directory.

```{r}

```

Use your credentials to establish a connection from R to the remote database.
```{r}

```

