---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
```

Q1
Load in the nyc_bikes data from the tsibbledata package. Have an initial look at it to see what you’re working with. Create three new columns: one that stores only the year the bike was used, one that stores only the month the bike was used, and one that stores the date. Use the data stored in start_time to create these new columns.
```{r}
nyc_bikes <- nyc_bikes %>% 
  mutate(start_year = year(nyc_bikes$start_time)) %>% 
  mutate(start_month = month(nyc_bikes$start_time)) %>% 
  mutate(start_date = date(start_time))

nyc_bikes
```

Q2
Summarise the number of bike hire counts by month. Make a plot of this data. *Hint: remember that to group time series (tsibble) data, you need to use index_by instead of group_by before your summarise function. What does this plot tell you about the time series? Do you think this downsampled data would be adequate to build a forecast with?
```{r}
nyc_bike_summary <- nyc_bikes %>% 
  index_by(start_month) %>% 
  summarise(hire_count = n())

nyc_bike_summary
  
```

```{r}
plot(nyc_bike_summary)

ggplot(nyc_bike_summary) +
  aes(x = start_month, y = hire_count) +
  geom_line()
```
The data indicates that the growth of hires correlates to the summer months and reverse for winter months. It would prove difficult to conduct series forecasting due to the fast that there is a lot of irregular patterns on a narrow data set.

Q3
Now Summarise the number of bike hire counts by date. Make a plot of this new aggregated data. What does this plot tell you about the time series? Would this data be preferrable for time series forecasting compared to the monthly data?
```{r}
nyc_bike_summary_by_date <- nyc_bikes %>% 
  index_by(start_date) %>% 
  summarise(hire_count = n())

nyc_bike_summary_by_date

plot(nyc_bike_summary_by_date)

nyc_bike_summary_by_date %>% 
  ggplot() +
  aes(x = start_date, y = hire_count) +
  geom_line()
```

Q4
create a new tibble which uses the fill_gaps() function to fill in missing values. You haven’t come across this in class, but you should be able to look it up and use it using the help. Think about what value you might want to fill the missing values with. Justify your choice.
Hint: think back to our missing values lesson. Do you want to leave them blank? Or do you want to impute each day with the median, last observation carried forward, etc.

Once you’ve done that, build your models.

```{r}
nyc_bikes_filled <- nyc_bike_summary %>%
  fill_gaps(hire_count = as.integer(median(hire_count)))

model_fit <- nyc_bikes_filled %>% 
  model(
    naive_model = NAIVE(hire_count),
    snaive_model = SNAIVE(hire_count),
    mean_model = MEAN(hire_count),
    arima_model = ARIMA(hire_count)
  )
model_fit
```
Q5
Now we have our model fit, build a forecast to predict bike use over the next four months. Plot your models alongside your data.
Hint: forecast parameter would be roughly 120 (30 days x 4 months)
```{r}
out_forecast <- model_fit %>% 
  fabletools::forecast(h = 120) 

out_forecast
```

```{r}
out_forecast %>% 
  autoplot(nyc_bikes_filled, level = NULL)
```
```{r}

```


Q6
Test your model accuracy : choose a training data set from your main dataset, build a forecast on the training set, and then plot the training set forecast against the real data. Calculate model accuracy.

```{r}

train <- nyc_bikes_filled %>% 
  mutate(month = month(start_date)) %>% 
  filter
  

```







Q7
Look at your forecast plots and accuracy values. Describe your results. Are your models a good fit for the data? If not, why not? What would you suggest doing with the data if you were expected to present these back to a client? For example, would you ask for more data? Would you test a different model?

(If my data is right) I would suggest that the original data set has too many large. There's large seasonal fluctuations and therefore the modeling would require richer data sets to establish any potential trends.



Q8
Make a simple ggplot (geom_point) which plots the start longitude and latitudes of each bike. Create a separate facet for each bike_id. Colour the dots in by month of use. What does this tell you about what month each bike was used most in?

Do the same for the end longitude and latitudes.
```{r}
leaflet(nyc_bikes) %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~start_long, lat = ~start_lat, radius = ~bike_id/10, weight = 10)
```


Q9
Create an interactive leaflet plot which plots the start points of the city bikes. Ensure it has at least markers to denote start points (taken from the nyc_bikes_spatial data). Feel free to add any additional features you wish.

```{r}
library(leaflet)

nyc_bikes_leaf <- nyc_bikes %>% 
  mutate_at(vars(bike_id, start_lat, start_long), as.numeric)
```

```{r}
leaflet(nyc_bikes_leaf) %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~start_long, lat = ~start_lat, clusterOptions = markerClusterOptions())
```

Q10
This is VERY much an extension task, and will take a bit of time (as well as googling) if you decide to attempt it.

Adapt your leaflet plot which adds lines showing the start and end point of each bike.

```{r}

```















