---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
```

Q1
Load in the nyc_bikes data from the tsibbledata package. Have an initial look at it to see what you’re working with. Create three new columns: one that stores only the year the bike was used, one that stores only the month the bike was used, and one that stores the date. Use the data stored in start_time to create these new columns.
```{r}
nyc_bikes <- nyc_bikes %>% 
  mutate(start_year = year(nyc_bikes$start_time)) %>% 
  mutate(start_month = month(nyc_bikes$start_time)) %>% 
  mutate(start_date = date(start_time))

nyc_bikes
```

Q2
Summarise the number of bike hire counts by month. Make a plot of this data. *Hint: remember that to group time series (tsibble) data, you need to use index_by instead of group_by before your summarise function. What does this plot tell you about the time series? Do you think this downsampled data would be adequate to build a forecast with?
```{r}
nyc_bike_summary <- nyc_bikes %>% 
  index_by(start_month) %>% 
  summarise(hire_count = n())

nyc_bike_summary
  
```

```{r}
plot(nyc_bike_summary)

ggplot(nyc_bike_summary) +
  aes(x = start_month, y = hire_count) +
  geom_line()
```
The data indicates that the growth of hires correlates to the summer months and reverse for winter months. It would prove difficult to conduct series forecasting due to the fast that there is a lot of irregular patterns on a narrow data set.

Q3
Now Summarise the number of bike hire counts by date. Make a plot of this new aggregated data. What does this plot tell you about the time series? Would this data be preferrable for time series forecasting compared to the monthly data?
```{r}
nyc_bike_summary %>% 
  index(~start_month) %>% 
  ggplot() +
  aes(x = start_date, y = hire_count) +
  geom_line()
```

Q4


```{r}
nyc_bikes_filled <- nyc_bike_summary %>%
  fill_gaps(hire_count = as.integer(median(hire_count)))

model_fit <- nyc_bikes_filled %>% 
  model(
    snaive_model = SNAIVE(hire_count),
    mean_model = MEAN(hire_count),
    arima_model = ARIMA(hire_count)
  )
model_fit
```
Q5
Now we have our model fit, build a forecast to predict bike use over the next four months. Plot your models alongside your data.
Hint: forecast parameter would be roughly 120 (30 days x 4 months)
```{r}
out_forecast <- model_fit %>% 
  fabletools::forecast(h = 120) 

out_forecast
```

```{r}
out_forecast %>% 
  autoplot(nyc_bike_summary, level = NULL)
```





























