---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

```{r}
ames <-read_csv("ames.csv")
```

Load the data again, clean_names(), and re-familiarise yourself with it
```{r}
glimpse(ames)
names(ames)
```
```{r}
clean_names(ames)
```


Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?
```{r}
ames %>% 
  ggplot(aes(x = Lot.Area)) + 
  geom_histogram(aes(..count..),col = "white") +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = Lot.Area$mean,
      sd = Lot.Area$sd
    ),
    col = "red"
  )
```

Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.
```{r}
bootstrap_resample <- ames %>% 
  rep_sample_n(size = 200, replace = TRUE, reps = 5000) %>% 
  summarise(
    mean_lot_area = mean(Lot.Area)
  )
```

```{r}
infer_ames <- ames %>% 
  specify(response = Lot.Area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")
infer_ames
```

Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
infer_ci_95 <-infer_ames %>% 
  get_ci(level = 0.95, type = "percentile")
infer_ci_95
```

```{r}
infer_ames %>% 
  visualise() +
  shade_confidence_interval(endpoints = infer_ci_95)
```

You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?
```{r}
infer_ci_99 <-infer_ames %>% 
  get_ci(level = 0.99, type = "percentile")
infer_ci_99
```
```{r}
infer_ames %>% 
  visualise() +
  shade_confidence_interval(endpoints = infer_ci_99)
```

Calculate the point estimate of the mean(lot_area)

```{r}
infer_ames %>% 
  summarise(mean(stat))
```

Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting].

[Hint - the current implementation of calculate(stat = "prop") in infer is slow! You can get around this by treating the mean in this way: add a new column via mutate(before_1920 = 

```{r}
ames %>% 
  mutate(before_1920 =  )
  


infer_resample_200 <- sample_200 %>% 
  specify(response = tenure) %>% 
  generate(reps = 50000, type = "bootstrap") %>% 
  calculate(stat = "mean")
infer_resample_200


```







