---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
data(msleep)
```

```{r}
head(msleep)
names(msleep)
view(msleep)
```

```{r}
msleep %>%
  ggplot(aes(x = sleep_total)) +
  geom_histogram(col = "white", bins = 25)
```
Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.
```{r}
msleep %>% 
  summarise(mean(sleep_total))
```

```{r}
omni <- msleep %>% 
  filter(vore == "omni")
omni

herbi <- msleep %>% 
  filter(vore == "herbi")
herbi

mean(herbi$sleep_total)
mean(omni$sleep_total)
```

```{r}
msleep %>%
  ggplot(aes(x = vore, y = sleep_total)) +
  geom_boxplot()
```
Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.
[Hint - think about creating an is_domesticated variable for the analysis]
```{r}
domesticated <- msleep %>% 
  filter(conservation == "domesticated") %>% 
  mutate(is_domesticated = "domesticated")
domesticated
```

```{r}
msleep %>% 
  mutate(is_domesticated = ifelse(conservation == "domesticated", "TRUE", "FALSE")) %>% 
  group_by(is_domesticated) %>% 
  summarise(n = n())
```

```{r}

```















specify() #specify the the variables of interest 
hypothesize() # state the null hypothesis  
generate() # what method will use to generate null hypotheses  
calculate() #statistic of interest


Ha:μ0>40%


```{r}

```



For the 3 business problems stated above, imagine we performed you got the following p-values (with the given significance levels) write out your interpretation of the results.

Coffee shop problem. Significance level: 0.05, calculated p-value: 0.07

Website company problem. Significance level: 0.01, p-value: 0.006

Manufacturing company problem. Significance level: 0.05, p-value: 0.55





