---
title: "R Notebook"
output: html_notebook
---

1. Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page
```{r}
library(tidyverse)
library(mosaicData)
library(ggiraphExtra)
library(GGally)
library(janitor)
library(fastDummies)
library(ggfortify)
```


```{r}
diamonds <- read_csv("diamonds.csv")

view(diamonds)
glimpse(diamonds)
summary(diamonds)
```

2. We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.

```{r}
diamonds %>% 
  select(carat, x, y, z) %>% 
  ggpairs()
```

3. So, we do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.
```{r}
diamonds_tidy <- diamonds %>% 
  select(-c("X1", "x", "y", "z"))

diamonds_tidy
```

```{r}
ggpairs(diamonds_tidy)
```


4. We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.
```{r}
model <- lm(price ~ carat, data = diamonds)
model
```
4. ii
Perform further ggplot visualisations of any significant correlations you find.
```{r}
diamonds %>% 
  ggplot(aes(x = price, y = carat)) +
  geom_point()
```

```{r}
diamonds %>% 
  ggplot(aes(x = price, y = carat)) +
  geom_boxplot()
```

```{r}
diamonds %>% 
  ggplot(aes(x = price, y = table)) +
  geom_point()
```

```{r}
diamonds %>% 
  ggplot(aes(x = price, y = depth)) +
  geom_point()
```
5. Shortly we may try a regression fit using one or more of the categorical predictors cut, clarity and color, so let’s investigate these predictors:
```{r}
diamonds_dummy <- diamonds %>% 
  dummy_cols(select_columns = c("cut", "clarity", "color"), remove_first_dummy = T) %>% 
  clean_names()
diamonds_dummy
```
6.
Going forward we’ll let R handle dummy variable creation for categorical predictors in regression fitting (remember lm() will generate the correct numbers of dummy levels automatically, absorbing one of the levels into the intercept as a reference level)
First, we’ll start with simple linear regression. Regress price on carat and check the regression diagnostics.
```{r}
lm(price ~ carat, data = diamonds)

par(mfrow = c(2,2))
plot(diamonds)
```


rough work
```{r}
model1 <- lm(price ~ carat + clarity + carat:clarity, data = diamonds)

summary(model1)
```

```{r}

```

