         ---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readr)

library(jsonlite)
```

1. Read in the state_income_data.csv file using the appropriate function.

```{r}
state_income_data <-read_csv("data/state_income_data.csv")
state_income_data
```

2.How do you specify your own column names when using read_csv()?
```{r}

state_income_data <-read_csv("data/state_income_data.csv", col_names = "Letter", "US State" etc etc)
```


3. Read in the cars.csv file and use the col_types() function to ensure you load in:

X1 as character
mpg, cyl, disp, hp as double
vs as logical

```{r}
read_csv("data/cars.csv", col_types = parse_logical)
```

```{r}

```


4. Read in the scotland.txt file using the appropriate function.
```{r}

scotland <- read_delim("data/scotland.txt", delim = ";", skip = 1)


```



5. How do you read text into a one element character vector?

No idea

```{r}
paste0(…, collapse = NULL)????
```


6. Read in the steam-200k-sample.csv file. Fix any problems you may encounter.

```{r}
read_csv("data/steam-200k-sample.csv", skip = 4)
```


7. Read in the historic_eu_payments.tsv file.

```{r}
eu_payments <- read_tsv("data/historic_eu_payments.tsv")
```

8. How do you read lines of text into a multi-element text vector?

```{r}
surnames <-read_lines("Data/surname.txt")

```

9. Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt

```{r}
read_file("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
```
 
```{r}
parse_json("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
```
 
```{r}
make_me_an_analyst_df <-fromJSON("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
```
 


Extension

A lot of Excel sheets you will encounter will contain more than one sheet. Try to write some code that reads in all the different sheets in the file green_bindle_consulting.xlsx.

[Hint: you will need to write a for loop]

```{r}
library(openxlsx)
library(readxl)
```

(Code from stack overflow but struggling to get tibble to work)

```{r}
read_all_excel_sheets <- read.xlsx("data/green_bindle_consulting.xlsx", tibble = FALSE) {}
sheets <- readxl::excel_sheets("data/green_bindle_consulting.xlsx")
    x <- lapply(sheets, function(X) readxl::read_excel("data/green_bindle_consulting.xlsx, sheet = X)
    if(!tibble) x <- lapply(x, as.data.frame)
    names(x) <- sheets
}


```

```{r}
my_sheets <- read_excel_allsheets("data/green_bindle_consulting.xlsx")
```




