---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(broom)
library(janitor)
library(modelr)
library(ggplot2)
library(GGally)
```

```{r}
juice <- read_csv("log_reg_data/orange_juice.csv") %>% 
  clean_names() %>% 
  mutate_if(is_character, as_factor)



summary(juice)
head(juice)
nrow(juice)

names(juice)
```

```{r}
split1 <- juice %>% 
  select(weekof_purchase, store_id, store, store7, list_price_diff, purchase)

split2 <- juice %>% 
  select(price_ch, price_mm, disc_ch, disc_mm, special_ch, special_mm, sale_price_mm, sale_price_ch, price_diff, purchase)



ggpairs(split2)
```

```{r}
ggpairs(split1)
```


```{r}
ggsave(juice, width = 10, height = 10, units = "in", device = "pdf")
```

```{r}
model1 <- lm(purchase ~ store7, data = juice)
model1
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

Text Mining

```{r}
library(tidytext)
library(tidyverse)
library(janeaustenr)
```
1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.
```{r}

str(prideprejudice)
str(sensesensibility)
pandp <- tibble(text = prideprejudice,
  sentence_no = 1:length(prideprejudice)) %>% 
  unnest_tokens(word, text)

sands <- tibble(text = sensesensibility,
  sentence_no = 1:length(sensesensibility)) %>% 
  unnest_tokens(word, text)
```
# Most popular words with Pride and Prejudice
```{r}
pandp %>% 
  count(word, sort = T) #without stop words

pandp %>% 
  count(word, sort = T) %>% 
  anti_join(stop_words) #with stop words
```
2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.

Most popular words in Sense and Sensibility
```{r}
sands %>% 
  count(word, sort = T) #without stop words

sands %>% 
  count(word, sort = T) %>% 
  anti_join(stop_words) #with stop words
```

together ?
```{r}
count(sands, word, sort = T) %>% 
  count(pandp, word, sort = T) %>% 
  anti_join(stop_words)
```

Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

```{r}
#Pride & prejudice
pandp_sentiments <-
pandp %>% 
  inner_join(get_sentiments("afinn"))
pandp_sentiments

#Sense and Sensibility
sands_sentiments <- 
sands %>% 
  inner_join(get_sentiments("afinn"))
sands_sentiments
```

```{r}
#Pride and prejudice
pandp_sentence_sentiments <- pandp_sentiments %>% 
  group_by(sentence_no) %>% 
  summarise(avg_sentiment = mean(value))
pandp_sentence_sentiments

#Sense and Sensesibility
sands_sentence_sentiments <- sands_sentiments %>% 
  group_by(sentence_no) %>% 
  summarise(avg_sentiment = mean(value))
sands_sentence_sentiments
```

```{r}
library(ggplot2)

#Pride and Prejudice
ggplot(pandp_sentence_sentiments) +
  aes(x = sentence_no, y = avg_sentiment) +
  geom_smooth()
#Sense and Sensibility
ggplot(sands_sentence_sentiments) +
  aes(sentence_no, y = avg_sentiment) +
  geom_smooth()
```

Extension
Taking your results above. Can you create a plot which visualises the differences between the books?

```{r}
plot_both <- rbind(pandp_sentence_sentiments, sands_sentence_sentiments)
```

```{r}
ggplot(plot_both) +
  aes(sentence_no, avg_sentiment) +
  geom_smooth()

ggplot(sands_sentence_sentiments) +
  aes(sentence_no, y = avg_sentiment) +
  geom_smooth()
```

```{r}
ggplot(pandp_sentence_sentiments) +
  aes(x = sentence_no, y = avg_sentiment) +
  geom_smooth(colour = "red")

ggplot(sands_sentence_sentiments) +
  aes(sentence_no, y = avg_sentiment) +
  geom_smooth(colour = "blue")
```





