---
title: "R Notebook"
output: html_notebook
---

```{r}
library(RPostgreSQL)

home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)

db_connect <- dbConnect(drv = PostgreSQL(), user = postgresql_username, password = postgresql_password, dbname = "omni_employees", host = "localhost")

rm(postgresql_username, postgresql_password)
```


```{sql connection=db_connect}
SELECT *
FROM employees
```





1. Find all the employees who work in the ‘Human Resources’ department.
```{sql connection=db_connect}
SELECT *
FROM employees
WHERE department = 'Human Resources'
```

2. Get the first name, last name, and country of the employees who work in the ‘Legal’ department
```{sql connection=db_connect}
SELECT 
  first_name,
  last_name,
  department
FROM employees
WHERE department = 'Legal'
```

3. Count the number of employees based in Portugal.
```{sql connection=db_connect}
SELECT 
  COUNT (*)
FROM employees
WHERE country = 'Portugal'
```

4. Count the number of employees based in either Portugal or Spain.
```{sql connection=db_connect}
SELECT 
  COUNT (*)
FROM employees
WHERE country = 'Portugal' OR country = 'Spain'
```

5. Count the number of pay_details records lacking a local_account_no
```{sql connection=db_connect}
SELECT
  COUNT (*)
FROM employees
WHERE pay_detail_id IS NOT NULL
```

6. Are there any pay_details record lacking both a local_account_no and iban number?
```{sql connection=db_connect}
SELECT *
FROM pay_details
WHERE (local_account_no = NULL) AND (iban = NULL)
```


7. Get a list of employees first names and last names ordered alphabetically by their last name (put any nulls last).
```{sql connection=db_connect}
SELECT
  last_name,
  first_name
FROM employees
ORDER BY last_name ASC NULLS LAST
```


8. Get a list of employees first names, last names and countries, ordered alphabetically first by their country and second by their last name (put any nulls last).
```{sql connection=db_connect}
SELECT
  first_name,
  last_name, 
  country
FROM employees
ORDER BY country ASC NULLS LAST, last_name ASC NULLS LAST
```


9. Find the top ten highest paid employees in the corporation.
```{sql connection=db_connect}
SELECT 
  first_name,
  last_name,
  salary
FROM employees
ORDER BY salary DESC NULLS LAST
LIMIT 10
```

10. Find the first name, last name and salary of the lowest paid of the employees in Hungary
```{sql connection=db_connect}
SELECT 
  first_name,
  last_name,
  salary
FROM employees
WHERE country = 'Hungary'
```

11. How many employees have a first name beginning with ‘F’?
```{sql connection=db_connect}
SELECT 
  COUNT (id) AS f_firstname
FROM employees
WHERE first_name LIKE 'F%'
```

12.Find all the details of any employees with a ‘yahoo’ e-mail address?
```{sql connection=db_connect}
SELECT *
FROM employees
WHERE email LIKE '%yahoo%'
```

13. Count the number of pension enrolled employees not based in either France or Germany.
```{sql connection=db_connect}
SELECT
  COUNT (id) AS pen_enrol_not_fra_ger
FROM employees
WHERE pension_enrol IS NOT NULL AND country IS NOT 'France'


(country IS NOT 'France' AND country IS NOT 'Germany')
```

14. Breakdown the numbers of employees enrolled, not enrolled and whose enrollment status is unknown in the corporation pension scheme.
```{sql connection=db_connect}
SELECT
  COUNT (employees) AS enrolled, not_enrolled, enrolled_unknown
FROM employees
WHERE pension_enrol IS NOT NULL = 'enrolled_unknown'
GROUP BY enrolled, not_enrolled, enrolled_unknown
```

15. What is the maximum salary among employees in the Engineering department who work 1.0 full-time equivalent hours?
```{sql connection=db_connect}
SELECT
  MAX(salary)
FROM employees
WHERE department = 'Engineering' AND fte_hours = 1.0
```

16. Obtain a count by department of the employees who started work with the corporation in 2003.
```{sql connection=db_connect}
SELECT 
  department,
  COUNT (department) AS dept_start_2003
FROM employees
WHERE start_date BETWEEN '2003-01-01' AND '2003-12-31'
GROUP BY department
```



```{r}
#dbDisconnect(db_connect)
```

