---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages("devtools")
```


```{r}
devtools::install_github("codeclan/CodeClanData")
```

```{r}
library(CodeClanData)
```

A data frame called beer

```{r}
data.frame(beer)
```

Finding the means of the beer attributes
```{r}
mean(beer$percent) 

mean(beer$calories)
#integer? Tried with L but haven't a notion why it's not working.

mean(beer$carbohydrates) 

```

Allocating beer name to variables within vectors?

```{r}
names(percent) <- beer

names(calories) <- beer

names(carbohydrates) <- beer
```


Reorder beers according to top and bottom 3: (establish any similarities)
a)percentage
b)calories
c)carbs
```{r}
(beer$percent, c(1, )
```



A matrix called temp

```{r}
matrix(temp)
```


#Analysis I would like to have done would be to find the average/mean temp for each month across each of the years.

#Understand which years or seasons had higher or lower temperatures




A list called game_of_thrones.

```{r}
list(game_of_thrones)
```

#Not sure what I would have done with this as not familiar with Game of Thrones other than count the difference in male to female characters. Also Matrix allude me completely.

```{r}
```

