---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(tidyverse)
```



```{r}
s_two_dice <- rolldie(2)
nrow(s_two_dice)
s_sum_equals_seven <- s_two_dice %>%
  filter(X1 + X2 == 7)
s_two_dice <- s_two_dice %>%
  mutate(total = X1 + X2)
```


```{r}
s_two_dice <- rolldie(2)

#get the total number of outcomes
size_s <- nrow(s_two_dice)
```

```{r}
#set the criteria I am interested in calculating the prob of:
total_seven <-s_two_dice %>% 
  filter(X1 + X2 == 7)
#get how many outcomes fir my criteria
size_seven <- nrow(total_seven)
```

```{r}
prob_total_seven <- size_seven / size_s
```

The prob of rolling 2 die and having it add up to 7 is 0.1666667



```{r}
s_die <- rolldie(1)
s_coin <- tosscoin(1)

s_total <- merge(s_die, s_coin)
s_total


```



# Permutations

```{r}
install.packages("gtools")
library(gtools)
```

```{r}
employees <- c("Alice", "Bob", "Carole", "David", "Elaine", "Fred", "Ghislaine", "Hua", "Inigo", "Hugo")
```


```{r}
senior_staff <- as_tibble(
  permutations(n = 10,
               r = 3,
               v = employees,
               repeats.allowed = FALSE)
)
```

```{r}
senior_staff <- senior_staff %>% 
  rename(CEO = V1,
         CTO = V2,
         COO = V3)

senior_staff
```

What is the probability of Alice being CEO and Bob being CTO?

```{r}
alice_and_bob <- senior_staff %>% 
  filter(CEO == "Alice", CTO == "Bob")
alice_and_bob
```

```{r}
prob_alice_and_bob <- nrow(alice_and_bob) / nrow(senior_staff)
prob_alice_and_bob
```


#TASK
```{r}
number_plates <- c("A", "B", "C", "D", "E")
```

```{r}

number_plates <- c("A", "B", "C", "D", "E")

no_repeats <- as_tibble(
  permutations(n = 5,
               r = 3,
               v = number_plates,
               repeats.allowed = FALSE))
no_repeats
```

```{r}
number_plates <- c("A", "B", "C", "D", "E")

repeats <- as_tibble(
  permutations(n = 5,
               r = 3,
               v = number_plates,
               repeats.allowed = TRUE))

repeats
```


# Combinations

card draws in R

```{r}
card_draws <- choose(52, 5)
card_draws
```
Colours 
```{r}
colours <- c("red", "blue", "yellow")

three_colour_permutations <- permutations(n = 3, 
                                          r = 3, 
                                          v = colours,
                                          repeats.allowed = FALSE)
```

```{r}
three_colour_permutations <- combinations(n = 3,
                                          r = 3,
                                          v = colours)
three_colour_permutations
```


#TASK
```{r}
flavours <- c("vanilla", "chocolate", "raspberry", "strawberry", "pistachio") 

diff_colour <- combinations(n = 5,
                            r = 3,
                            v = flavours,
                            repeats.allowed = FALSE)
diff_colour
```

```{r}
flavours <- c("vanilla", "chocolate", "raspberry", "strawberry", "pistachio") 

diff_colour <- combinations(n = 5,
                            r = 3,
                            v = flavours,
                            repeats.allowed = TRUE)
diff_colour
```

```{r}
numbers <- choose(50,6)
numbers


```

```{r}


ten_tickets <- (10/numbers)
ten_tickets
```

# Complement

```{r}
s_four_coins <-
tosscoin(4) %>% 
  mutate(
    number_of_heads = as.numeric(toss1 == "H") +
      as.numeric(toss2 == "H") +
      as.numeric(toss3 == "H") +
      as.numeric(toss4 == "H")
  ) %>% 
  filter(number_of_heads >= 2)

```

```{r}
11/16
```


```{r}
15/16
```


Prob of tossing at least one head and one tail
```{r}
tosscoin(4) %>% 
  mutate(
    number_of_heads = as.numeric(toss1 == "H") +
      as.numeric(toss2 == "H") +
      as.numeric(toss3 == "H") +
      as.numeric(toss4 == "H"),
    number_of_tails = as.numeric(toss1 == "T") +
      as.numeric(toss2 == "T") +
      as.numeric(toss3 == "T") +
      as.numeric(toss4 == "T")
) %>% 
  filter(number_of_heads >= 1 & number_of_tails >= 1)

```

```{r}
14/16
```

Union

Probability that first die is even and second die is 5?

```{r}
rolldie(2) %>% 
  filter(X1 %% 2 == 0 | X2 == 5)
```
result/rolldie(2)
```{r}
21/36
```

Task - 10 mins
Calculate probabilities for each event below:
first_die_even
second_die_5
first_die_even AND second_die_5
Then use these probabilities in the expression from above
prob(A∪B)=prob(A)+prob(B)−prob(A∩B)
and check you get the same probability for prob(first_die_even OR second_die_5)
prob(first_die_even OR second_die_5) as we obtained from the last block of code. (

```{r}
rolldie(2) %>% 
  filter(X1 %% 2 == 0)

18/36
  
```

```{r}
rolldie(2) %>% 
  filter(X2 == 5)
6/36

```


```{r}
rolldie(2) %>% 
  filter(X1 %% 2 == 0 & X2 == 5)

3/36
```

```{r}
0.5 + 0.167 - 0.083
```










































